Article title

### 2019-07-10 NAR_DRAFT.tex
check in figure 1
add figuref 1 caption

\begin{figure}[t]
\begin{center}
\includegraphics{figures/wes_left_plot.pdf}
\end{center}
\caption{Caption for figure within column.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/kl_figure.png}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}

>>>>

%\begin{figure}[t]
%\begin{center}
%\includegraphics{figures/wes_left_plot.pdf}
%\end{center}
%\caption{Caption for figure within column.}
%\label{NAR-fig1}
%\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/fig1.pdf}
\end{center}
\caption{Model performance on 500X simulated whole exome.
\textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
\textbf{(b)} Convergence of the estimated mutation signature to the simulated signature with mutations in descending order of confidence.
\textbf{(d)} \bkmcomment{signatures or one single calibration curve. This figure could also lose current c and d and have all three calibration curves to the right. KL and signatures in another figure?}
}
\label{NAR-fig2}
\end{figure*}
